### 2017-02-26 2017mergingmerges/section/03-Definition.tex
Treat records like maps from labels to fields

% -----------------------------------------------------------------------------
\subsubsection{Injection}
Fig.~\ref{fig:Process:Eval:Inject} defines the judgment forms and rules for injection.
Injection is used by the other parts of evaluation to \emph{inject} stream values into a process' input buffer.

@@

The judgment form ($\ProcInject{p}{c}{v}{p'}$) means that the process $p$ has the value $v$ inserted to the input buffer for channel $c$, resulting in the updated process $p'$.

>>>>

% -----------------------------------------------------------------------------
\eject{}
\subsubsection{Injection}
Fig.~\ref{fig:Process:Eval:Inject} gives the rules for injecting values into processes. The judgment form $\ProcInject{p}{v}{c}{p'}$ reads ``given process $p$, injecting value $v$ into channel $c$ yields a new process $p'$''. The @injects@ form is similar, but for sets of processes rather than a single one.

Rule (InjectValue) handles the injection of a single value into a single process.

% Injection is used by the other parts of evaluation to \emph{inject} stream values into a process' input buffer.

@@
